---
title: "Live Session Unit 11 Assignment"
author: "Anthony Dalton"
date: "November 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fpp)
```

# a) Read in data and plot visitors data
```{r}
data(visitors)
plot(visitors)
# You can definitely see seasonality and that the amount of visitors trends up over time.
```

# b) Classical decomposition to calculate the trend cycle
```{r}
fitd <- decompose(visitors) 
plot(fitd)
```

# c) The results support the interpretation from part a, the trend definitely is heading up while there is seasonality

# d) Computing and plotting of the seasonally adjusted data
```{r}
eeadj <- seasadj(fitd) 
plot(eeadj)
```

# e) Change one observation to be an outlier
```{r}
# Adding 500 to the third value and replotting the chart
eeadj[3] = 675.4
plot(eeadj)
# You can see a very large spike in the dataset
```

#  f) Placement of the outlier doesn't matter, adding 500 to the middle value
```{r}
eeadj[120] = 675.4
# Spikes the same
plot(eeadj)
```

# g) Use STL to decompose the series.
```{r}
fit <- stl(visitors, s.window=5) 
plot(fit) 
```